### 2017-05-15 paper/paper.tex
Fixed missing word

The Schulze Method is a method used mainly to determine results in single-winner elections but can also be used to provide rankings and elect multiple candidates in a single election \autocite{Schulze2011}. Ballots are identical to those of the Single Transferable Vote (see figure~\ref{fig:stv ballot} on page~\pageref{fig:stv ballot}). The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate  \autocite{johnson2005}. As mentioned, this method relies on comparing the preferences of every candidate to one another as shown in table~\ref{tab:pairwise comparison matrix}. If there is a Condorcet winner the process is simple: declare the Condorcet winner a winner and run another iteration without that candidate. Repeat this process until all seats are filled. However, there can be Condorcet ties, where there is no Condorcet winner. There are multiple methods used for resolving Condorcet ties, with one of them being the Schulze Method.

>>>>

The Schulze Method is a method used mainly to determine results in single-winner elections but can also be used to provide rankings and elect multiple candidates in a single election \autocite{Schulze2011}. Ballots are identical to those of the Single Transferable Vote (see figure~\ref{fig:stv ballot} on page~\pageref{fig:stv ballot}). The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate will win \autocite{johnson2005}. As mentioned, this method relies on comparing the preferences of every candidate to one another as shown in table~\ref{tab:pairwise comparison matrix}. If there is a Condorcet winner the process is simple: declare the Condorcet winner a winner and run another iteration without that candidate. Repeat this process until all seats are filled. However, there can be Condorcet ties, where there is no Condorcet winner. There are multiple methods used for resolving Condorcet ties, with one of them being the Schulze Method.
